Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-04 paper/paper.qmd
Almost finished introduction and discussion and updated idealized survey section with Google Form link

Overview paragraph

This led to us investigate the following question in our paper: what are the differences in homicide case information like the year and city the homicide took place and the victims’ perceived characteristics (age, sex, and race) between solved and unsolved homicides in one of the 2 of the largest cities in the United States, Chicago and Los Angeles, from 2010 to 2017?

Estimand paragraph

@@

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

@@

Weaknesses and next steps should also be included.

- Since the dataset was compiled in 2018, we currently do not know if any of the homicide cases have been solved as of 2024 and how many.

@@

### Idealized Survey Design
We will creating our survey using Google Form due to it being the survey platforn people are the most familiar with in terms of the user interface. When designing our survey we also considered different respondent biases that could occur. For example, response order bias occurs when respondents choose answers based on their order [@citeStantcheva]. To address this bias, for questions with ordinal scales we will be reversing the ordering at random [@citeStantcheva]. Another bias that could occur is social desirability bias, in which respondents would pick an answer in order to be perceived positively by others [@citeStantcheva]. To address this bias, we will reassure respondents in the survey that their response will not be shared with other members on their team and their response will be only seen by the research team and that they can choose to contact us and withdraw their answers anytime [@citeStantcheva]. Following this, our survey will ask the following type of questions:

@@

Some limitations with using a survey is that even though we made it so that all questions are required to be answered and minimize non-response errors [@citetellingstories], @citeStantcheva mentions that survey attrition becomes a problem. Attrition occurs when respondents decide to not complete the survey over the course of completing the survey [@citeStantcheva]. @citeStantcheva also noted respondent could have biases like social desirability bias and response order bias when responding to a survey. Our survey design aimed to mitgate these biases but these biases could still occur with respondents's answers.

@@

**Demographic Questions**
1. What is your email? (Open-ended question)

@@

4. What is your ranking on your team? ____ (Open-ended question)

5. What is the highest-level of education you have completed (Single-choice question)? No formal education/kindergarten only, Elementary, Middle School, High School, General Equivalency Diploma (GED) or equivalent, Some college, Associate's Degree, Bachelor's Degree, Master's Degree, Professional degree, Doctoral degree

**Job-related Questions**
6. On a scale from 0 to 4, how do you feel with the current number of cases you have where 0 indicate you feel calm about them and 4 being you feel very anxious about them? (Single-choice question) 0, 1, 2, 3, 4

@@

8. What are some of the reason you may close a homicide case without making any arrest? (Open-ended question)

@@

@@

>>>>

TO REMOVE: The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate [Done]; 2) some detail about what the paper is about [Done]; 3) a clear gap that needs to be filled [Done]; 4) what was done [Done]; 5) what was found; 6) why it is important; 7) the structure of the paper. A reader should be able to read only the introduction and know what was done, why, and what was found. Likely 3 or 4 paragraphs, or 10 per cent of total.

On November 20, 2024, Chicago Mayor Brandon Johnson announced that the Chicago Police Department had the highest homicide clearance rate, which are cases that are solved, as of recent years at almost 54% [@citechicagonews]. Despite celebrating this accomplishment, @citechicagonews found that if only cases with arrest was considered and not closed cases where the police believed they have identified the perpetrator without an arrest being made, their clearance rate was actually 23% this year. This concern about homicide clearance rate was expressed by @citeguardian where they mentioned that homicide clearance rates from 1980 to 2020 have decreased from 71% to 50% in the United States (US). As of 2023, there are currently no up-to-date database keeping track of homicide resolutions and current crime databases do not indicate the victim's race and what led to the homicide, making it difficult to figure out why homicides are going unsolved [@citeguardian]. This raises the following question: what are the differences in homicide case information like the year and city the homicide took place and the victims’ perceived characteristics (age, sex, and race) between solved and unsolved homicides in one of the 2 of the largest cities in the United States, Chicago and Los Angeles, from 2010 to 2017?

Our estimand is the homicide case information like the victim's demographic information (age, sex, and race) and the year and city the homicide occurred in/on if the homicide case is unsolved or solved.

In this paper, to see what factors could impact the likelihood of a homicide case going unsolved, we analyzed data provided by The Washington Post [@datahomicides] that were compiled by their reporters on homicide cases and their status from 2010 to 2017. Previously, The Washington Post has used the data they compiled to construct a map and pinpointing places unsolved homicides occur [@citewashingtonpostmap]. However, specific analysis looking at the differences in case characteristics between specific two US cities like Chicago and Los Angeles has not been done previously. In our findings, it shows that

@@

TO REMOVE: Some questions that a good discussion would cover include (each of these would be a sub-section of something like half a page to a page): What is done in this paper? [Done] What is something that we learn about the world? What is another thing that we learn about the world? What are some weaknesses of what was done? What is left to learn or how should we proceed in the future?

In @sec-results, we analyzed homicide case information like the victim's age, sex, and race and the year and city the homicide case occurred to see if there were any differences between homicide case information between unsolved and solved homicides from the year 2010 to 2017. We also built a Bayesian logistic regression model in @sec-model-results, to see the likelihood of the homicide case information impacting the homicide case outcome of going unsolved.

## Disportionate number of homicide victims in unsolved cases are Black and Hispanic

## Age of the homicide victim likely does not impact the outcome of their case being unsolved however their gender may

## Chicago likely to have more unsolved cases than Los Angeles

@@

- Since the dataset was compiled in 2018, we currently do not know if any of the homicide cases have been solved as of 2024 and how many. 
- Recommendations includes compiling a new dataset for the years 2018 to 2024 similar to what The Washington Post did.

@@

### Idealized Survey Design
We will create our survey using Google Form since it is the survey platforn people are the most familiar with in terms of the user interface. When designing our survey we also considered different respondent biases that could occur. For example, response order bias occurs when respondents choose answers based on their order [@citeStantcheva]. To address this bias, for questions with ordinal scales we will be reversing the ordering at random [@citeStantcheva]. Another bias that could occur is social desirability bias, in which respondents would pick an answer in order to be perceived positively by others [@citeStantcheva]. To address this bias, we will reassure respondents in the survey that their response will not be shared with other members on their team and their response will be only seen by the research team and that they can choose to contact us and withdraw their answers anytime [@citeStantcheva]. Following this, our survey will ask the following type of questions:

@@

Some limitations with using a survey is that even though we made it so that all demographic questions and job-related questions are required to be answered and minimize non-response errors [@citetellingstories], @citeStantcheva mentions that survey attrition becomes a problem. Attrition occurs when respondents decide to not complete the survey over the course of completing the survey [@citeStantcheva]. @citeStantcheva also noted respondent could have biases like social desirability bias and response order bias when responding to a survey. Our survey design aimed to mitgate these biases but these biases could still occur with respondents's answers.

### Link to Idealized Survey

A link to what the survey may look like can be found here: [https://forms.gle/TrDBVuQPvF4ap8Wq8](https://forms.gle/TrDBVuQPvF4ap8Wq8)

@@

**Demographic Questions**

1. What is your email? (Open-ended question)

@@

4. What is your ranking in your department? ____ (Open-ended question)

5. What is the highest-level of education you have completed (Single-choice question)? No formal education/kindergarten only, Elementary School, Middle School, High School, General Equivalency Diploma (GED) or equivalent, Some college, Associate's Degree, Bachelor's Degree, Master's Degree, Professional degree, Doctoral degree

**Job-related Questions**

6. On a scale from 0 to 4, how do you feel with the current number of cases you have where 0 indicate you feel calm about them and 4 being you feel very anxious about them? (Single-choice question) 0, 1, 2, 3, 4

@@

8. What are some of the reason you may close a homicide case without making any arrest? If you can, feel free to bring up past cases. (Open-ended question)

@@

**Others**

@@

11. Do you have any thoughts or comments? (Open-ended question)
